Procurements of the Canadian Government, Runaway Military Contracts

### 2024-12-02 paper/paper.qmd
updated paper

```{r fig-results}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

@@

# Format the table for Quarto using kableExtra
combined_results %>%
  select(model, term, estimate, std.error, statistic, p.value) %>%
  rename(
    Model = model,
    Term = term,
    Estimate = estimate,
    `Std. Error` = std.error,
    `t-Statistic` = statistic,
    `p-Value` = p.value
  ) %>%
  kable(format = "html", digits = 3, align = "c", caption = "Model Results Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

>>>>

```{r fig-results}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Model Results Summary
#| fig-align: center

@@

# Determine the output format
output_format <- knitr::opts_knit$get("rmarkdown.pandoc.to")

# Choose styling based on output format
if (output_format == "latex") {
  combined_results %>%
    select(model, term, estimate, std.error, statistic, p.value) %>%
    rename(
      Model = model,
      Term = term,
      Estimate = estimate,
      `Std. Error` = std.error,
      `t-Statistic` = statistic,
      `p-Value` = p.value
    ) %>%
    kable(booktabs = TRUE, caption = "Model Results Summary") %>%
    kable_styling(latex_options = c("striped", "hold_position"))
} else {
  combined_results %>%
    select(model, term, estimate, std.error, statistic, p.value) %>%
    rename(
      Model = model,
      Term = term,
      Estimate = estimate,
      `Std. Error` = std.error,
      `t-Statistic` = statistic,
      `p-Value` = p.value
    ) %>%
    kable(format = "html", digits = 3, align = "c", caption = "Model Results Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
}
```
